%-------------------------------------------------------------------------------
% Summaries
%-------------------------------------------------------------------------------
\newcommand{\BartendingSummary}{I’m an experienced bartender with a passion for creating exceptional cocktails and providing excellent customer service. I have a proven track record of working efficiently in high-pressure environments while maintaining a friendly atmosphere and work environment. I am dedicated, reliable, and a team player looking to work with like-minded individuals who are committed to the success of the establishment.}

\newcommand{\ServingSummary}{I am an experienced service industry professional with a strong passion for providing exceptional customer service and creating memorable experiences for guests. With a proven ability to work efficiently in fast-paced environments, I excel in multitasking and maintaining a positive, welcoming atmosphere. I am dedicated, reliable, and a team player, committed to contributing to the success of the establishment.}

\newcommand{\FireSummary}{Self-motivated wildland firefighter with six months of experience as a U.S. Forest Service employee. Dedicated and physically fit individual looking to extend my passion for the outdoors and serving the public through a wildland firefighting position. I have a proven track record working in a team environment in high stress situations, and am eager to contribute my efforts towards wildfire prevention, supression, containment, and restoration efforts. Qualified FFT2 and EMT-Basic.}